---
title: "Process_GrowthRateData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_GrowthRateData.Rmd processes and combines PICO_Cleaned_MCData.Rds from Data/CleanedData/CleanedMCData folder and both BalticPhotoperiod_Processed_PigmentsAll.Rds and BalticPhotoperiod_Processed_PigmentsExp.Rds from Data/ProcessedData/ProcessedPigmentsData. This .Rmd generates BalticPhotoperiod_Processed_GrowthRateAll.Rds (stored in Data/ProcessedData/ProcessesGrowthRateData folder) and 2 plots (stored in Output/Figures folder).

# Load Libraries and set Project Variables

```{r load libraries} 
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(ggpubr)
library(caret)
library(reshape2)
library(gcookbook)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)
library(scales)
library(minpack.lm) #Standard 'nls' framework that uses 'nls.lm' for fitting
library(data.table)
library(googledrive)
library(googlesheets4)
library(tidyverse)
library("patchwork") # merging plots

```

```{r set project variables}
Project <- "SynBaltic"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthRateData")
DataIn <- file.path("..", "Data", "CleanedData", "CleanedMCData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, full.names = TRUE)
```

```{r read file}
MultiCultiGrowthFile <- "../Data/CleanedData/CleanedMCData/PICO_Cleaned_MCData.Rds"

MultiCultiGrowthFileName <- str_split(string = MultiCultiGrowthFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 

MultiCultiGrowth <- readRDS(MultiCultiGrowthFile)  %>%
  ungroup()
```

# Select revelant variables and preparing for further analysis

```{r}
MultiCultiGrowth<-MultiCultiGrowth %>% 
  dplyr::select(c(Tube, ExpDate, MC, Run, SampleID, Strain, Par_ue, Photoperiod, WL, O2, LightShape, PARPhotonDose_day, OD720_Lmu_se, OD720_Lmu_corr, deltaOD_Lmu_se, deltaOD_Lmu_corr))
  
# MultiCultiGrowth<-MultiCultiGrowth %>% 
#   mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA77G"~"PC-rich_077"))

```


# Growth rate per day

```{r}
MultiCultiGrowth<-MultiCultiGrowth %>% 
  mutate(deltaOD_Lmu_corr=deltaOD_Lmu_corr*24)
```

# Adding facets labels

```{r}
# MultiCultiGrowth<-MultiCultiGrowth %>% 
#   mutate(Oxygen=case_when(O2==21~"250~µM",
#          O2==0~"2.5~µM"))
```


```{r}
MultiCultiGrowth %>%
  #filter(WL != "WW") %>% 
  ggplot() +
  geom_point(aes(x = Strain, y = deltaOD_Lmu_corr), size = 3.5, alpha = 0.9, show.legend = F) +
  ggh4x::facet_nested(cols = vars(Tube)) +
  theme_bw()

MultiCultiGrowth %>%
  #filter(WL != "WW") %>% 
  ggplot() +
  geom_point(aes(x = Strain, y = OD720_Lmu_corr), size = 3.5, alpha = 0.9, show.legend = F) +
  ggh4x::facet_nested(cols = vars(Tube)) +
  theme_bw()
```

```{r}
# lab1=c(expression("PC-rich_077"), expression("PE-rich_127"))
# 
# MultiCultiGrowth %>%
#   mutate(WLNum = if_else(WL == "WW", 750, as.numeric(WL))) %>%
#   filter(WL != "WW") %>%
#   ggplot() +
#   geom_point(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), shape = as.factor(Strain)), size = 4, show.legend = T) +
#   geom_line(aes(x = WLNum, y = deltaOD_Lmu_corr, colour = as.factor(Strain), linetype = as.factor(Strain)), show.legend = F) +
#   # geom_errorbar(aes(x = WLNum, ymin = deltaOD_Lmu_corr - deltaOD_Lmu_se, ymax = deltaOD_Lmu_corr + deltaOD_Lmu_se, colour = as.factor(Strain)), width=20, size=0.3, show.legend = F) +
#   
#   stat_wl_strip(aes(x = WLNum), ymin = -Inf, ymax = -0.025, alpha = 0.5) +
#   scale_fill_identity() +
#   scale_colour_manual(values = c("palegreen3", "brown4"), name="", labels = lab1) +
#   scale_shape_manual(values = c(16, 18), name="", labels = lab1) +
#   scale_linetype_manual(values = c("solid", "dashed"), name="", labels = lab1) +
#   labs(y = "Chlorophyll-specific exponential growth rate " ~ "("~d^-1~")", x = "Growth wavelength (nm)") +
#   #scale_x_continuous(breaks=seq(0, 200, by = 50)) +
#   #coord_cartesian(xlim = c (0, 200)) +
#   #coord_cartesian(xlim = c (400, 800)) +
#   # guides(colour = FALSE) +
#   #ggh4x::facet_nested(rows = vars(O2), cols = vars(Strain), labeller = label_parsed) +
#   labs(y = "µ " ~ "("~d^-1~")", x = "Wavelength (nm)") +
#   ggh4x::facet_nested(rows = vars(factor(Oxygen, levels=c("250~µM","2.5~µM"))), labeller = label_parsed) +
#  #ggh4x::facet_nested(cols = vars(Strain), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         panel.spacing.x = unit(0.4, 'cm'),
#         axis.text = element_text(size=12),
#         axis.text.x = element_text(size=12),
#         axis.title = element_text(size=16),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=12),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         legend.background = element_rect(fill="transparent"),
#         legend.key = element_blank(),
#         legend.title = element_blank(),
#         legend.position = c(0.10,0.90),
#         legend.text = element_text(size=10))

```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_GrowthRate",".png",sep = "")), height=5.5, width= 6,  dpi = 300, limitsize = TRUE)
```



-----------------------------------------------------------------------------------------------------------


# Calculated Anova and Tukey test

```{r calculated statistics}
MultiCultiGrowth2<-MultiCultiGrowth %>% 
  filter(WL != "WW")

MCGrowthRateStats<-rbind(MultiCultiGrowth2, MultiCultiGrowth2) #I created double data here

MCGrowthRateStats$O2 <- factor(MCGrowthRateStats$O2)
MCGrowthRateStats$WL <- factor(MCGrowthRateStats$WL)
MCGrowthRateStats$Strain <- factor(MCGrowthRateStats$Strain)

# Two way Anova with interactions
model<-aov(deltaOD_Lmu_corr~O2*WL*Strain, data=MCGrowthRateStats)
AnovaTest_GrowthRate<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
TukeyHSDTest_GrowthRate<-TukeyHSD(model, which = c("O2", "WL", "Strain"))
```



# Save RDS that create stats and tables

```{r}
saveRDS(AnovaTest_GrowthRate, file.path(TableRdsPath, paste(Project, "Anova_GrowthRate.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

saveRDS(TukeyHSDTest_GrowthRate, file.path(TableRdsPath, paste(Project, "HSD_GrowthRate.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Cleaning the environment

```{r}
rm(MCGrowthRateStats, model, MultiCultiGrowth2)
```

# Save Rds for further analysis

```{r save rds}
saveRDS(MultiCultiGrowth, file.path(DataOut, paste(Project, "Processed_GrowthRate.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```


------------------------------------------------------------------------------------------------------------------
-------------------------------------------------------------------------------------------------------------------

