---
title: "MarineBotanyExp"
author:
- Sylwia Sliwinska-Wilczewska
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

MarineBotanyExp.Rmd imports: 
Culture_culture catalog from google sheet, Growth catalog from google sheet,
PAMAS.....

# Load libraries

```{r load libraries}
library(kableExtra)
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(ggspectra)
library(ggpubr)
library(caret)
library(gcookbook)
library(scales)
```

# Set Project Variables

```{r set project variables}
Project <- "Salinity"
DataOut <- file.path("..", "Data", "CleanedData", "AllelopathyExp")

PlotsPath <- file.path("..", "Output", "Plots", "AllelopathyExp")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS", "AllelopathyExp")
RDSTablePath <- file.path("..", "Output", "TablesRDS", "AllelopathyExp")
```

# Import MetaDataCatalog

Load Allelopathy_MetaDataCatalog
```{r load local catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

# this is the URL or ID of a Sheet readable by anyone (with a link)

CultureCatalog <- read_sheet("https://docs.google.com/spreadsheets/d/1D-dchdt_DQUj2v7TBA-RUkBCvIn4eBX9adO-E7h6xNk/edit?gid=0#gid=0") %>%
  #mutate(Date = as.numeric(Date)) %>%
  mutate(StartDate = ymd(`StartDate`)) %>% 
  mutate(Measuredate = ymd(`Measuredate`)) 
```

```{r}

GrowthMeta <- CultureCatalog %>%
group_by(SampleID) %>%
  arrange(Measuredate) %>%
  mutate(E_days = as.numeric((Measuredate - StartDate[1]))) %>%
ungroup() 
```



# Calculate the mean

```{r}
# GrowthMetamean<-GrowthMeta %>%
#   group_by(SampleID) %>%
#   mutate(meanOD750 = mean(OD750)) %>%
#   mutate(sdOD750 = sd(OD750)) %>%
#   ungroup()
```


# Create preliminary plot

```{r preliminary plot}
GrowthMeta %>%
  #filter(Target_Species == "Cyanobium") %>% 
  #filter(Treatment == "Stationary") %>% 
  ggplot() +
  geom_point(aes(x = E_days, y =OD750), show.legend = T) +
  geom_smooth(aes(x = E_days, y =OD750), method = lm, show.legend = F, alpha = 0.1) +
  # geom_errorbar(aes(x = Dilution, ymin = meanCount104-sdCount104, ymax = meanCount104+sdCount104)) +
  # labs(y = "Number of cells (N" ~10^4 ~mL^-1~")", x = "Culture concentration (mL)") +
  #scale_x_continuous(breaks=seq(0, 7, by = 1)) +
  # coord_cartesian(ylim = c (0, 12)) +
  # ggh4x::facet_nested(cols = vars(Strain), rows = vars(Salinity), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()
```




---------------------------------------------- PAMAS -------------------------------------------------------

# IMPORT PAMAS DATA

# Set project variables and list files in the extracted folder

```{r set project variables, warning = FALSE, echo = FALSE}
# Project <- "BalticPhotoperiod"
# zip_file <- file.path("..", "Data", "RawData", "PamasData.zip")
# 
# 
# CountFiles <- unzip(zip_file, list = TRUE)
# CountFiles <- CountFiles[grepl(".txt$", CountFiles$Name), "Name"]
# print(CountFiles)
# 
# FileID <- "PAMAS"
# FileEncode <- "UTF-8" 
# HeaderRows <- 9
# DelimCS <- "\t"
```

# Read fread_plus function

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
# # Define function to read and process each file
# fread_plus <- function(Flnm, FileEncode, Delim) {
#   con <- unz(zip_file, Flnm)
#   
#   # Read the file using read.table
#   data <- read.table(con, skip = HeaderRows, encoding = FileEncode, sep = Delim, header = TRUE)
#   
#   # Use tryCatch to handle errors during the closing of the connection
#   tryCatch(
#     close(con),
#     error = function(e) {
#       warning("Error closing connection: ", e$message)
#     })
#   
#   data <- data %>%
#     mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
#   return(data)
# }
# 
# # Use map_df to read and process all files in CountFiles
# CountTidy <- CountFiles %>%
#   map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = DelimCS))
```

# Clean up the filename column

```{r clean up df, warning = FALSE, echo = FALSE}
# CountTidy <- CountTidy %>% 
#   mutate(Filename = str_remove(string = Filename, pattern = ".txt")) %>%
#   mutate(Filename = str_remove(string = Filename, pattern = "../PamasData/")) %>%
#   separate(Filename, into = c("Date", "Strain", "Dilution", "Device"), sep = "([\\/\\/\\_\\_\\_\\_])", remove = FALSE) %>% 
#   mutate(Date = as.double(`Date`)) %>%
#   mutate(Date = ymd_hm(`Date`))
```

# Tidy PAMAS df

```{r tidy TargetPamasData, warning = FALSE, echo = FALSE}

# NewNames <- c("PAMASDate", "Time", ">0.70",">0.80", ">0.90", ">1.00", ">1.20", ">1.50", ">2.00",">3.00", ">4.00", ">5.00", ">6.00", ">7.00", ">10.00", ">12.00",
# ">15.00",">20.00", "Filename", "Date","Strain", "Dilution", "Device", "cdatetime")
# 
# OldNames <- colnames(CountTidy)
# 
# PamasTidy <- CountTidy %>%
# rename_with(~NewNames[which(OldNames == .x)], .cols = OldNames) %>%
#   mutate(datetime = paste(PAMASDate, Time),
#          datetime = mdy_hms(datetime))
```

# Tidy PAMAS df

```{r}
# PamasTidy <- PamasTidy %>%
# mutate(`S0.7` = as.numeric(`>0.70`) - as.numeric(`>0.80`),
#        `S0.8` = as.numeric(`>0.80`) - as.numeric(`>0.90`),
#        `S0.9` = as.numeric(`>0.90`) - as.numeric(`>1.00`),
#        `S1.0` = as.numeric(`>1.00`) - as.numeric(`>1.20`),
#        `S1.2` = as.numeric(`>1.20`) - as.numeric(`>1.50`),
#        `S1.5` = as.numeric(`>1.50`) - as.numeric(`>2.00`),
#        `S2.0` = as.numeric(`>2.00`) - as.numeric(`>3.00`),
#        `S3.0` = as.numeric(`>3.00`) - as.numeric(`>4.00`),
#        `S4.0` = as.numeric(`>4.00`) - as.numeric(`>5.00`),
#        `S5.0` = as.numeric(`>5.00`) - as.numeric(`>6.00`),
#        `S6.0` = as.numeric(`>6.00`) - as.numeric(`>7.00`),
#        `S7.0` = as.numeric(`>7.00`) - as.numeric(`>10.00`),
#        `S10.0` = as.numeric(`>10.00`) - as.numeric(`>12.00`),
#        `S12.0` = as.numeric(`>12.00`) - as.numeric(`>15.00`),
#        `S15.0` = as.numeric(`>15.00`) - as.numeric(`>20.00`),
#        `S20.0` = as.numeric(`>20.00`))
# 
# PamasTidy <- PamasTidy %>%
#   pivot_longer(., cols = c("S0.7", "S0.8", "S0.9", "S1.0", "S1.2", "S1.5", "S2.0", "S3.0", "S4.0", "S5.0", "S6.0", "S7.0", "S10.0", "S12.0", "S15.0", "S20.0"), names_to = "CellSize_um", values_to = "Count") %>%
#   mutate_at("CellSize_um", str_replace, "S", "") %>%
#   mutate(CellSize_um = as.numeric(CellSize_um)) %>%
#   group_by(CellSize_um, Strain, Dilution) %>%
#   mutate(meanCount = mean(Count), 
#          sdCount = sd(Count)) %>%
#   ungroup() %>%
#   select(c(PAMASDate, Filename, Date, Strain, Dilution, cdatetime, CellSize_um, Count, meanCount, sdCount))
```

# Rename variables for consistency

```{r}
# PamasTidy<-PamasTidy %>% 
#   rename(ObsDate=Date) %>%
#   rename(FilenamePAMAS=Filename) %>% 
#   select(-c(cdatetime, PAMASDate))
```

# Create preliminary plot

```{r preliminary plot}
# PamasTidy %>%
#   mutate(meanCount104 = meanCount/10000) %>%
#   mutate(sdCount104 = sdCount/10000) %>%
#   filter(CellSize_um < 4) %>% 
#   ggplot() +
#   geom_point(aes(x = Dilution, y =meanCount104, label = Strain)) +
#   geom_errorbar(aes(x = Dilution, ymin = meanCount104-sdCount104, ymax = meanCount104+sdCount104)) +
#   labs(y = "Number of cells (N" ~10^4 ~mL^-1~")", x = "Culture concentration (mL)") +
#   scale_y_continuous(breaks=seq(0, 12, by = 4)) +
#   coord_cartesian(ylim = c (0, 12)) +
#   ggh4x::facet_nested(rows = vars(CellSize_um), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
#   theme_bw()
```




# Save Rds for further analysis if needed

```{r save rds}
# saveRDS(PigmentsClarioOlisCorr, file.path(DataOut, paste(Project, "Imported_PigmentsClarioOlisCorrData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```



# Correlations from Polish flowcytometer (BD Accuri) and Polish Spec if needed

```{r}
# GrowthClarioN <- GrowthClario %>%
#   mutate(OD750N = case_when(
#           Strain == 'BA77G' ~ 5766620.03*OD750+5146.44,
#          Strain == 'BA56G' ~ 815627.77*OD750-6499.89, 
#          Strain == 'BA48R' ~ 110516351.55*OD750-568505.87,
#          Strain == 'BA127R' ~ 124271003.22*OD750-1691760.02))
```


