---
title: "Import_PigmentandCorrelationData"
author:
- Sylwia Sliwinska-Wilczewska
- Mireille Savoie
- Naaman M. Omar 
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_PigmentData.Rmd imports: 
PAMAS files from Data/RawData/PAMASData.zip folder, 
ClarioPigments from ClarioPigments Catalog,
ClarioGrowth from ClarioGrowth Catalog,
GrowthCurveData from BalticPhotoperiod_Processed_GrowthCurve.Rds, 
and OlisJazData from BalticPhotoperiod_Processed_OlisSpectraAll.Rds

and stored in Data/ImportedData/ImportedPigmentData folder as: 
BalticPhotoperiod_Imported_PigmentData.Rds

This script contains Spearman correlations performed for cell counts taken from PAMAS and OD680 taken from ClarioSTAR (cell/mL). Additionally, Spearman correlations were made for the pigment content obtained using the filter method (measured on ClarioSTAR) with the absorbance obtained from Olis (pigment content - ug/mL). The cell counts data was added to the GrowthCurveData file (the cell count was calculated based on OD680 measured on MC; cell/mL). The obtained cell number was used to convert pigments (based on Olis) per cell (fg/cell). If it make sense...

The tables with the compiled correlations were saved in the BalticPhotoperiod\Output\TablesRDS folder as:
BalticPhotoperiod_Table_GrowthCorrelation.Rds,
BalticPhotoperiod_Table_PigmentsCorrelation.Rds


# Load libraries

```{r load libraries}
library(kableExtra)
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(ggspectra)
library(ggpubr)
library(caret)
library(gcookbook)
library(scales)
```

# Set Project Variables

```{r set project variables}
Project <- "Sam"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedPamassData")

FigPath <- file.path("..", "Output", "Figures")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")
RDSTablePath <- file.path("..", "Output", "TablesRDS")


```



Pearson Correlation Coefficient and Linear Regression and coefficient of determination or R²
https://www.datacamp.com/tutorial/linear-regression-R



---------------------------------------------- PAMAS -------------------------------------------------------

# IMPORT PAMAS CORRELATION DATA

# Set project variables and list files in the extracted folder

```{r set project variables, warning = FALSE, echo = FALSE}
Project <- "Sam"
zip_file <- file.path("..", "Data", "RawData", "PamasData.zip")

# List files in the extracted folder with a ".txt" extension
CountFiles <- unzip(zip_file, list = TRUE)
CountFiles <- CountFiles[grepl(".txt$", CountFiles$Name), "Name"]
print(CountFiles)

FileID <- "PAMAS"
FileEncode <- "UTF-8" 
HeaderRows <- 9
DelimCS <- "\t"
```

# Read fread_plus function

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
# Define function to read and process each file
fread_plus <- function(Flnm, FileEncode, Delim) {
  con <- unz(zip_file, Flnm)
  
  # Read the file using read.table
  data <- read.table(con, skip = HeaderRows, encoding = FileEncode, sep = Delim, header = TRUE)
  
  # Use tryCatch to handle errors during the closing of the connection
  tryCatch(
    close(con),
    error = function(e) {
      warning("Error closing connection: ", e$message)
    })
  
  data <- data %>%
    mutate(Filename = Flnm, CDateTime = ymd_hms(file.info(zip_file)$ctime)) 
  return(data)
}

# Use map_df to read and process all files in CountFiles
CountTidy <- CountFiles %>%
  map_df(~fread_plus(Flnm = ., FileEncode = FileEncode, Delim = DelimCS))
```

# Clean up the filename column

```{r clean up df, warning = FALSE, echo = FALSE}
CountTidy <- CountTidy %>% 
  mutate(Filename = str_remove(string = Filename, pattern = ".txt")) %>%
  mutate(Filename = str_remove(string = Filename, pattern = "../PamasData/")) %>%
  separate(Filename, into = c("Date", "Strain", "Dilution", "Device"), sep = "([\\/\\/\\_\\_\\_\\_])", remove = FALSE) %>% 
  mutate(Date = as.double(`Date`)) %>%
  mutate(Date = ymd_hm(`Date`))
```

# Tidy PAMAS df

```{r tidy TargetPamasData, warning = FALSE, echo = FALSE}
# figure out how to read and rename these columns from the file rather than manually
NewNames <- c("PAMASDate", "Time", ">0.70",">0.80", ">0.90", ">1.00", ">1.20", ">1.50", ">2.00",">3.00", ">4.00", ">5.00", ">6.00", ">7.00", ">10.00", ">12.00",
">15.00",">20.00", "Filename", "Date","Strain", "Dilution", "Device", "cdatetime")

OldNames <- colnames(CountTidy)

PamasTidy <- CountTidy %>%
rename_with(~NewNames[which(OldNames == .x)], .cols = OldNames) %>%
  mutate(datetime = paste(PAMASDate, Time),
         datetime = mdy_hms(datetime))
```

# Tidy PAMAS df

```{r}
PamasTidy <- PamasTidy %>%
mutate(`S0.7` = as.numeric(`>0.70`) - as.numeric(`>0.80`),
       `S0.8` = as.numeric(`>0.80`) - as.numeric(`>0.90`),
       `S0.9` = as.numeric(`>0.90`) - as.numeric(`>1.00`),
       `S1.0` = as.numeric(`>1.00`) - as.numeric(`>1.20`),
       `S1.2` = as.numeric(`>1.20`) - as.numeric(`>1.50`),
       `S1.5` = as.numeric(`>1.50`) - as.numeric(`>2.00`),
       `S2.0` = as.numeric(`>2.00`) - as.numeric(`>3.00`),
       `S3.0` = as.numeric(`>3.00`) - as.numeric(`>4.00`),
       `S4.0` = as.numeric(`>4.00`) - as.numeric(`>5.00`),
       `S5.0` = as.numeric(`>5.00`) - as.numeric(`>6.00`),
       `S6.0` = as.numeric(`>6.00`) - as.numeric(`>7.00`),
       `S7.0` = as.numeric(`>7.00`) - as.numeric(`>10.00`),
       `S10.0` = as.numeric(`>10.00`) - as.numeric(`>12.00`),
       `S12.0` = as.numeric(`>12.00`) - as.numeric(`>15.00`),
       `S15.0` = as.numeric(`>15.00`) - as.numeric(`>20.00`),
       `S20.0` = as.numeric(`>20.00`))

PamasTidy <- PamasTidy %>%
  pivot_longer(., cols = c("S0.7", "S0.8", "S0.9", "S1.0", "S1.2", "S1.5", "S2.0", "S3.0", "S4.0", "S5.0", "S6.0", "S7.0", "S10.0", "S12.0", "S15.0", "S20.0"), names_to = "CellSize_um", values_to = "Count") %>%
  mutate_at("CellSize_um", str_replace, "S", "") %>%
  mutate(CellSize_um = as.numeric(CellSize_um)) %>%
  group_by(CellSize_um, Strain, Dilution) %>%
  mutate(meanCount = mean(Count), 
         sdCount = sd(Count)) %>%
  ungroup() %>%
  select(c(PAMASDate, Filename, Date, Strain, Dilution, cdatetime, CellSize_um, Count, meanCount, sdCount))
```

# Rename variables for consistency

```{r}
PamasTidy<-PamasTidy %>% 
  rename(ObsDate=Date) %>%
  rename(FilenamePAMAS=Filename) %>% 
  select(-c(cdatetime, PAMASDate))
```

# Create preliminary plot

```{r preliminary plot}
PamasTidy %>%
  mutate(meanCount104 = meanCount/10000) %>%
  mutate(sdCount104 = sdCount/10000) %>%
  filter(CellSize_um < 4) %>% 
  ggplot() +
  geom_point(aes(x = Dilution, y =meanCount104, label = Strain)) +
  geom_errorbar(aes(x = Dilution, ymin = meanCount104-sdCount104, ymax = meanCount104+sdCount104)) +
  labs(y = "Number of cells (N" ~10^4 ~mL^-1~")", x = "Culture concentration (mL)") +
  scale_y_continuous(breaks=seq(0, 12, by = 4)) +
  coord_cartesian(ylim = c (0, 12)) +
  ggh4x::facet_nested(rows = vars(CellSize_um), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()
```
# Removed unnecessary files from the environment

```{r removed unnecessary files from the environment}
rm(CountTidy)
```

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_lPAMAS",".png",sep = "")), height=5, width= 8,  dpi = 300, limitsize = TRUE)
```

# Save rds for further analysis if needed

```{r save rds}
# saveRDS(PamasTidy, file.path(DataOut, paste(Project, "Imported_PamasData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


