---
title: "Process_GrowthCurveData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_GrowthCurveData.Rmd separately processes and combines all .Rds from Data/ImportedData/ImportedMCData folder. This .Rmd generates BalticPhotoperiod_Processed_GrowthCurve.Rds (stored in Data/ProcessedData/ProcessedGrowthCurveData folder) and GrowthCurve_SupPlot.png (stored in Output/Plots folder).

# Load Libraries and set Project Variables

```{r load libraries} 
# library(xts)
# library(signal)

library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(data.table)
library(googledrive)
library(googlesheets4)
library(tidyverse)
library("patchwork") # merging plots
```

```{r set project variables}
Project <- "SynBaltic"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthCurveData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

## Read Data
```{r data files}
MCFiles <- list.files(path = file.path("..", "Data", "ImportedData", "ImportedMCData"), full.names = TRUE)
MCFiles
```

```{r read data}

MCData <- readRDS(file = MCFiles[1]) |>
  ungroup() |>
  mutate(DeltaOD = OD680 - OD720)

  colnames(MCData)
  
MCDataAll <- map_df(MCFiles, readRDS) |>
  ungroup() |>
  mutate(DeltaOD = OD680 - OD720)
```

```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}

MCDataAll$ToD = sub("\\..*", "", MCDataAll$ToD)
MCDataAll$time = sub("\\..*", "", MCDataAll$time)

MCDataAll <- MCDataAll %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) 
  
MCDataAll <- MCDataAll %>%   
  group_by(SampleID, Day, ToD, time_h, Run) %>% 
  summarize(Run, SampleID, Strain, ExpDate, Filename, Tube, time_h, ToD, Day, ExpDate, Actinic_par, OD680, OD720, DeltaOD, Par_ue, Photoperiod, O2, WL, LightShape, ExpEndDate, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(DeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, DeltaOD)) %>% 
  unique()
```

# Rename column names for consistency

```{r}
MultiCultiDataAll<-MCDataAll %>% 
  rename(E_days=Day) %>% 
  rename(FilenameMC=Filename) %>% 
  rename(Time_h=time_h)
```

# Add facets labels and change strain name to create plot

```{r add facets labels and change strain names}
# MultiCultiDataAll$facetsPar_ue = factor(MultiCultiDataAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
# MultiCultiDataAll$facetsPhotoperiod = factor(MultiCultiDataAll$WL, labels = c("Photoperiod~(h)"))

# MultiCultiDataAll <- MultiCultiDataAll %>% 
#     mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA77G"~"PC-rich_077")) %>% 
#     mutate(Oxygen=case_when(O2==21~"250~µM",
#          O2==0~"2.5~µM"))
```


# Create GrowthCurve plot

```{r create GrowthCurve plot, warning = FALSE}
data_textA <- data.frame(facetsPar_ue = c("PAR~(µmol~photons~m^{-2}~s^{-1})"), Par_ue = c(900), Photoperiod  = c(8), facetsPhotoperiod = c("Photoperiod~(h)"), label = c('A'))

OD680<-MultiCultiDataAll %>%
  # filter(WL!= "WW") %>% 
  # filter(Time_h <= 192) %>% 
  ggplot() +
  
  #geom_area(aes(x = Time_h, y = meanActinic_par_h), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = Time_h/24, y = meanOD680_h, colour = as.factor(Strain)), size = 0.5, show.legend = T) +
  scale_colour_discrete(type=c("palegreen3", "brown4")) +
  #scale_colour_discrete(type=c("palegreen3", "brown4"), name="") +
  labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (d)") +

  #ggh4x::facet_nested(cols = vars(WL), rows = vars(factor(O2, levels=c("21","0"))), labeller = label_parsed) +
    ggh4x::facet_nested(cols = vars(Tube), labeller = label_parsed) +
  
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        #panel.spacing.x = unit(0.4, 'cm'),
        axis.text = element_text(size=12),
        axis.text.x = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.title = element_blank(),
        legend.position = c(0.09,0.90),
        legend.text = element_text(size=10))
OD680
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_GrowthCurve_OD680",".png",sep = "")), height=5, width= 8,  dpi = 300, limitsize = TRUE)
```




-------------------------------------------------------------------------------------------------------------------
-------------------------------------------------------------------------------------------------------------------

```{r, warning = FALSE, fig.height = 9, fig.width = 12}
# ggp<- OD680+OD720
# ggp                           
```

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_GrowthCurve_OD680720",".png",sep = "")), height=9, width= 12,  dpi = 300, limitsize = TRUE)
```




-------------------------------------------------# Logistic fits till Pmax-------------------------------------------------------


```{r set project variables}
Project <- "SynBaltic"
#DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedGrowthRateData")
DataIn <- file.path("..", "Data", "CleanedData", "CleanedMCData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

# List and read files

```{r Exported Rmd only first time in session}
list.files(path = DataIn, full.names = TRUE)
```

```{r read file}
MultiCultiGrowthFile <- "../Data/CleanedData/CleanedMCData/PICO_Cleaned_MCData.Rds"

MultiCultiGrowthFileName <- str_split(string = MultiCultiGrowthFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds") 

MultiCultiGrowth <- readRDS(MultiCultiGrowthFile)  %>%
  ungroup()
```

# Select revelant variables and preparing for further analysis

```{r}
MultiCultiGrowth<-MultiCultiGrowth %>% 
  dplyr::select(c(Tube, ExpDate, MC, Run, SampleID, Strain, Par_ue, Photoperiod, WL, O2, LightShape, PARPhotonDose_day, OD720_Lmu_se, OD720_Lmu_corr, deltaOD_Lmu_se, deltaOD_Lmu_corr, tubedata, deltaOD_logistic_predict))

# MCGrowthRate<-MultiCultiGrowth %>% 
#   mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA77G"~"PC-rich_077"))

```

```{r unnest, preparing df to preparing final plot, echo=FALSE, warning = FALSE}

augmentedMCGrowthRateFitDeltaOD<-MultiCultiGrowth  %>%
  unnest(deltaOD_logistic_predict) %>%
  select(c(deltaOD, time, .fitted)) 

augmentedMCGrowthRateTubedata<-MultiCultiGrowth  %>%
  unnest(tubedata)

augmentedMCGrowthRateTubedata<-augmentedMCGrowthRateTubedata %>% 
  select(-c(deltaOD_logistic_predict))

```

# Merge tubedata and fit prediction - DeltaOD

```{r warning = FALSE}

MCGrowthRateFitDeltaOD <- augmentedMCGrowthRateFitDeltaOD %>%
  left_join(., augmentedMCGrowthRateTubedata, by = c("deltaOD" = "deltaOD", "time" = "time"))
MCGrowthRateFitDeltaOD<-MCGrowthRateFitDeltaOD %>% 
  rename(fittedDeltaOD = .fitted) 

MCGrowthRateFitData<-MCGrowthRateFitDeltaOD

```


```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}

MCGrowthRateFitData$ToD = sub("\\..*", "", MCGrowthRateFitData$ToD)
MCGrowthRateFitData$time = sub("\\..*", "", MCGrowthRateFitData$time)

MCGrowthRateFitData <- MCGrowthRateFitData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/1000) %>% 
  rename(time_h=time) 
  

#colnames(MCGrowthRateFitData)

MCGrowthRateFitData <- MCGrowthRateFitData %>%   
  group_by(SampleID, Day, ToD, time_h) %>% 
  summarize(deltaOD, time_h, fittedDeltaOD, OD720, Tube, ExpDate, MC, Run, SampleID, Strain, Par_ue, Photoperiod, WL, O2, LightShape, PARPhotonDose_day, OD720_Lmu_se, OD720_Lmu_corr, deltaOD_Lmu_se, deltaOD_Lmu_corr, ToD, Day, Actinic_par, OD680, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(deltaOD), meanfittedDeltaOD_h = mean(fittedDeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, deltaOD, fittedDeltaOD)) %>% 
  unique()
```


# Adding facet labels

```{r}
# MCGrowthRateFitData$facetsPar_ue = factor(MCGrowthRateFitData$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
# MCGrowthRateFitData$facetsPhotoperiod = factor(MCGrowthRateFitData$WL, labels = c("Photoperiod~(h)"))
# MCGrowthRateFitData$facetsStrain = factor(MCGrowthRateFitData$WL, labels = c("Strain"))
```


# Create GrowthCurve plot with fits

```{r create GrowthCurve plot, warning = FALSE}

MCGrowthRateFitData %>%
  # filter(WL!= "WW") %>% 
  # filter(Par_ue == 180) %>% 
  ggplot() +
  #geom_area(aes(x = time_h, y = meanActinic_par_h), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = Time_h, y = meanDeltaOD_h, colour = as.factor(Strain)), size = 0.7, alpha = 0.2, show.legend = F, MultiCultiDataAll) +
  geom_line(aes(x = time_h, y = meanfittedDeltaOD_h, colour = as.factor(Strain)), size = 0.7, alpha = 0.9, show.legend = T) +
  #scale_colour_discrete(type=c("palegreen3", "brown4"), name="") +
  # scale_y_continuous(breaks=seq(0, 1, by = 0.25)) +
  # coord_cartesian(ylim = c(0, 1.0)) +
  labs(y = "Optical density (\u0394 OD)", x = "Elapsed time (h)") +
    ggh4x::facet_nested(cols = vars(Tube), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=11))
```


# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_GrowthCurve_FitPmax",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```




-------------------------------------------------# Whole Logistic fits --------------------------------------------------------

```{r set project variables}
Project <- "SynBaltic"
# DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

## Read Data
```{r data files}
MCFilesFit <- list.files(path = file.path("..", "Data", "ProcessedData", "ProcessedMCDataLogisticFit"), full.names = TRUE)
MCFilesFit
```

```{r read data}

# MCData <- readRDS(file = MCFilesFit[1]) |>
#   ungroup()
  
MCDataAllFit <- map_df(MCFilesFit, readRDS) |>
  ungroup() 
```


# Select revelant variables and preparing for further analysis

```{r}
MultiCultiGrowth<-MCDataAllFit %>% 
  dplyr::select(c(Tube, ExpDate, MC, Run, SampleID, Strain, Par_ue, Photoperiod, WL, O2, LightShape, PARPhotonDose_day, tubedata, deltaOD_logistic_predict))


# MultiCultiGrowth<-MultiCultiGrowth %>% 
#   mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA77G"~"PC-rich_077"))

MCGrowthRate<-MultiCultiGrowth 


```

```{r unnest, preparing df to preparing final plot, echo=FALSE, warning = FALSE}

augmentedMCGrowthRateFitDeltaOD<-MCGrowthRate  %>%
  unnest(deltaOD_logistic_predict) %>%
  select(c(deltaOD, time, .fitted)) 

augmentedMCGrowthRateTubedata<-MCGrowthRate  %>%
  unnest(tubedata)

augmentedMCGrowthRateTubedata<-augmentedMCGrowthRateTubedata %>% 
  select(-c(deltaOD_logistic_predict))

```

# Merge tubedata and fit prediction - OD720
```{r warning = FALSE}

MCGrowthRateFitDeltaOD <- augmentedMCGrowthRateFitDeltaOD %>%
  left_join(., augmentedMCGrowthRateTubedata, by = c("deltaOD" = "deltaOD", "time" = "time"))
MCGrowthRateFitDeltaOD<-MCGrowthRateFitDeltaOD %>% 
  rename(fittedDeltaOD = .fitted) 

MCGrowthRateFitData<-MCGrowthRateFitDeltaOD

```



```{r Import Run and calculate mean OD, echo = FALSE, warning = FALSE}

MCGrowthRateFitData$ToD = sub("\\..*", "", MCGrowthRateFitData$ToD)
MCGrowthRateFitData$time = sub("\\..*", "", MCGrowthRateFitData$time)

MCGrowthRateFitData <- MCGrowthRateFitData %>% 
  mutate(ToD=as.numeric(ToD)) %>% 
  mutate(time=as.numeric(time)) %>% 
  mutate(Actinic_par = Actinic_par/2000) %>% 
  rename(time_h=time) 
  

#colnames(MCGrowthRateFitData)

MCGrowthRateFitData <- MCGrowthRateFitData %>%   
  group_by(SampleID, Day, ToD, time_h) %>% 
  summarize(deltaOD, time_h, fittedDeltaOD, OD720, Tube, ExpDate, MC, Run, SampleID, Strain, Par_ue, Photoperiod, WL, O2, LightShape, PARPhotonDose_day, ToD, Day, Actinic_par, OD680, meanActinic_par_h = mean(Actinic_par), meanOD680_h = mean(OD680), meanOD720_h = mean(OD720), meanDeltaOD_h = mean(deltaOD), meanfittedDeltaOD_h = mean(fittedDeltaOD)) %>%
  ungroup() %>% 
  select(-c(Actinic_par, OD680, OD720, deltaOD, fittedDeltaOD)) %>% 
  unique()
```


# Adding facet labels

```{r}
MCGrowthRateFitData$facetsPar_ue = factor(MCGrowthRateFitData$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
MCGrowthRateFitData$facetsPhotoperiod = factor(MCGrowthRateFitData$WL, labels = c("Photoperiod~(h)"))
MCGrowthRateFitData$facetsStrain = factor(MCGrowthRateFitData$WL, labels = c("Strain"))
```


# Create GrowthCurve plot with fits

```{r create GrowthCurve plot, fig.height = 8, fig.width = 8, warning = FALSE}

data_textB <- data.frame(facetsPar_ue = c("PAR~(µmol~photons~m^{-2}~s^{-1})"), Par_ue = c(900), Photoperiod  = c(8), facetsPhotoperiod = c("Photoperiod~(h)"), label = c('B'))

ODFit<-MCGrowthRateFitData %>%
  filter(Run != 77) %>% 
  ggplot() +
  #geom_area(aes(x = time_h, y = meanActinic_par_h), size = 0.1, fill = "tan1", alpha = 0.6) +
  geom_line(aes(x = time_h/24, y = meanDeltaOD_h, colour = as.factor(Strain)), size = 0.4, alpha = 0.5, show.legend = F) +
  geom_line(aes(x = time_h/24, y = meanfittedDeltaOD_h, colour = as.factor(Strain)), size = 0.8, alpha = 0.9, show.legend = T) +
  geom_text(data=data_textB, aes(x=2, y=0.3, label=label), size=6) +
  
  scale_colour_discrete(type=c("palegreen3", "brown4"), name="") +
  scale_y_continuous(breaks=seq(0, 0.4, by = 0.1)) +
  # coord_cartesian(ylim = c(0, 1.0)) +
  # labs(y = "Logistic fits of chlorophyll proxy"~OD[680]~"-"~OD[720]~"(\u0394 OD)", x = "Elapsed time (h)") +
  scale_x_continuous(breaks=seq(0, 15, by = 3)) +
  coord_cartesian(xlim = c(0, 14), ylim = c(0, 0.4)) +
  labs(y = "Logistic fits of chlorophyll proxy ("~OD[680]~"-"~OD[720]~")", x = "Elapsed time (d)") +
  #ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, factor(Par_ue, levels=c("900","600","300","180","90","30"))), labeller = label_parsed) +
  
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=11))
ODFit
```

# Save plot 

```{r save plot}
# ggsave(file = file.path(FigPath, paste("SFig_GrowthCurve_Fit",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

```{r, warning = FALSE, fig.height = 9, fig.width = 12}
ggp<- ODDelta+ODFit
ggp                           
```

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_GrowthCurve_ODDeltaFit",".png",sep = "")), height=9, width= 12,  dpi = 300, limitsize = TRUE)
```

# Save Rds for further analysis

```{r save rds}
saveRDS(MultiCultiDataAll, file.path(DataOut, paste(Project, "Processed_GrowthCurve.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(MultiCultiDataAll)
```



